\section{Work Experience}
\cventry{10.2015--\\present~}{Senior Software Developer, Team Lead}{\href{http://grfc.ru}{\underline{<<General Radio Frequency Centre>>}}, Federal State Unitary Enterprise}{Moscow, Russia}{}{Telecommunications\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Head of the development of the \href{https://online.grfc.ru}{\underline{web portal}} for digital documents management; integration with internal enterprise IT-systems; integration with \href{http://taxcom.ru/dokumentooborot/}{\underline{service for digital invoice exchange}} (Java Core; Java EE: EJB, JMS, JPA, Servlet, JAX-WS; HTML/CSS/JS; Oracle DBMS).
\item Head of the development of the \href{https://online.grfc.ru/sign.verify}{\underline{digital signature validation service}};  integration with internal enterprise IT-systems and \href{https://e-trust.gosuslugi.ru/}{\underline{Ministry of Telecom and Mass Communications of the Russian Federation services}} (Java Core; Java EE: EJB, JMS, Servlet; HTML/CSS/JS).
\item Design and develop internal enterprise system for digital documents management, frequency requests processing, integration with third-party software for calculation of electromagnetic compatibility (Java Core: Swing; Groovy; Java EE: EJB, JMS, JPA; Oracle DBMS).
\item Continuous Integration management (Git/Gitolite, Jenkins, Gradle).
\end{itemize}}

\cventry{10.2014--10.2015~}{Senior Software Developer}{\href{http://grfc.ru}{\underline{<<General Radio Frequency Centre>>}}, Federal State Unitary Enterprise}{Moscow, Russia}{}{Telecommunications\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Design and develop \href{https://online.grfc.ru}{\underline{web portal}} for digital documents management; integration with internal enterprise IT-systems (Java Core; Java EE: EJB, JMS, JPA, Servlet, JAX-WS; HTML/CSS/JS; DBMS Oracle).
\item Design and develop \href{https://online.grfc.ru/sign.verify}{\underline{digital signature validation service}}; integration with internal enterprise IT-systems (Java Core; Java EE: EJB, JMS, Servlet, JAX-WS; HTML/CSS/JS).
\end{itemize}}

\cventry{09.2008--10.2014~}{Senior Software Developer, Team Lead}{\href{http://openinfotech.ru}{\underline{<<Open Information Technologies>>}}, LLC}{Moscow, Russia}{}{Information technologies: software development and integration\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Design and develop <<Social Insurance>> information system, which is used by Fund of Social Insurance (FSI) --- big government structure of Russian Federation, as system architect and deputy project manager (Delphi; Java Core; DBMS HyTech; Sphinx Search).
\item Design, develop and optimize for highload \href{http://fz122.fss.ru}{\underline{FSI web portal}} as system architect of full-text search and lead OLAP-developer (PHP; HTML/CSS/JS; Java Core; DBMS HyTech; Sphinx Search).
\item Design, develop and optimize for highload \href{http://f4.fss.ru}{\underline{FSI web-service}} to process digital signed financial statements as system architect (PHP; HTML/CSS/JS; DBMS HyTech).
\item Design and develop framework, which is used for interaction between common ERP systems and \href{http://www.openinfotech.ru/index.php?service=4&subs=11}{\underline{converter of financial reports}} from Russian national standards to IFRS and GAAP, as lead developer (C; Delphi).
\end{itemize}}
\cventry{}{}{}{}{}{
\begin{itemize}
\item Design and develop \href{http://www.openinfotech.ru/index.php?service=4&subs=10}{\underline{electronic payment processing system}} as system architect (PHP; HTML/CSS/JS; C; DBMS MySQL/PostgreSQL/HyTech).
\item Design and develop software to process information about copyright and related rights in intellectual property as system architect (PHP; HTML/CSS/JS; DBMS HyTech and MongoDB).
\item Continuous integration management (Jenkins).
\end{itemize}}

\cventry{09.2007--07.2013~}{Research/Teaching Associate}{National Research Nuclear University <<MEPhI>>, \href{http://kaf36.ru}{\underline{<<Information Systems and Technologies>>} department}}{Moscow, Russia}{}{Science and education\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Teaching experience:
  \begin{itemize}
  \item <<Algorithms and Data Structures>> (lections and labs);
  \item <<Programming Languages and Compilators>> (lections and labs);
  \item <<Optimization Methods>> (lections and labs);
	\item <<Numerical Computing>> (labs);
  \item <<Game Theory and Operation Research>> (lections).
  \end{itemize}
\item Supervise course work and assignments of undergraduate students.
\item Participate in department's research work.
\item Create and deliver tutorial and lab session material for undergraduate students.
\end{itemize}}

\cventry{10.2005--09.2008~}{Junior, Middle Software Developer}{<<New information systems and technologies>>, JSC}{Moscow, Russia}{}{Information technologies: software development and integration\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Design and develop <<Social Insurance>> information system, which is used by Fund of Social Insurance (FSI) --- big government structure of Russian Federation, as lead developer (Delphi; DBMS HyTech).
\item Design and develop \href{http://fz122.fss.ru}{\underline{FSI web portal}} as lead OLAP-developer and software architect of application for delivery financial statements from insurants to FSI (PHP; HTML/CSS/JS; СУБД HyTech).
\end{itemize}}