\section{Work Experience}
\cventry{09.2008--\\present~}{Software Developer, Team Lead, System Architect}{\href{http://openinfotech.ru}{\underline{<<Open Information Technologies>>}}, LLC}{Moscow, Russia}{}{Information technologies: software development and integration\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Design and develop \href{http://rkn.gov.ru/it/register/?id=90538}{\underline{<<Social Insurance>>}} information system, which is used by Fund of Social Insurance (FSI) --- big government structure of Russian Federation, as system architect and co-project manager.
\item Design, develop and optimize for highload \href{http://fz122.fss.ru}{\underline{FSI internet portal}} as system architect of full-text search and lead OLAP-developer.
\item Design, develop and optimize for highload \href{http://f4.fss.ru}{\underline{FSI web-service}} to process digital signed financial statements as system architect.
\item Design and develop framework, which is used for interaction between common ERP systems and \href{http://www.openinfotech.ru/index.php?service=4&subs=11}{\underline{converter of financial reports}} from Russian national standards to IFRS and GAAP, as lead developer.
\item Design and develop \href{http://www.openinfotech.ru/index.php?service=4&subs=10}{\underline{electronic payment processing system}} as system architect.
\item Design and develop application server to process information about copyright and related rights in intellectual property as system architect.
\end{itemize}}

\cventry{09.2007--07.2013~}{Research/Teaching Associate}{National Research Nuclear University <<MEPhI>>, \href{http://kaf36.ru}{\underline{<<Information Systems and Technologies>>} department}}{Moscow, Russia}{}{Science and education\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Teaching experience:
  \begin{itemize}
  \item <<Algorithms and Data Structures>> (lections and labs);
  \item <<Programming Languages and Compilators>> (lections and labs);
  \item <<Optimization Methods>> (lections and labs);
	\item <<Numerical Computing>> (labs);
  \item <<Game Theory and Operation Research>> (lections).
  \end{itemize}
\item Supervise course work and assignments of undergraduate students.
\item Participate in department's research work.
\item Create and deliver tutorial and lab session material for undergraduate students.
\end{itemize}}

\cventry{10.2005--09.2008~}{Software Developer}{<<New information systems and technologies>>, JSC}{Moscow, Russia}{}{Information technologies: software development and integration\newline{}
\underline{Responsibilities}:
\begin{itemize}
\item Design and develop \href{http://rkn.gov.ru/it/register/?id=90538}{\underline{<<Social Insurance>>}} information system, which is used by Fund of Social Insurance (FSI) --- big government structure of Russian Federation, as lead developer.
\item Design and develop \href{http://fz122.fss.ru}{\underline{FSI internet portal}} as lead OLAP-developer and software architect of application for delivery financial statements from insurants to FSI.
\end{itemize}}