\section{Professional Skills}
\cvitem{}{Tools actively used in last year marked \textbf{bold}; actively used over a year ago presented with regular font; studied but not used actively marked \textit{italic}.}
\cvitem{OS}{\textbf{Linux (RedHat-based)}, \textbf{Windows}, \textit{FreeBSD}}
\cvitem{Languages}{\textbf{Java}, \textbf{SQL}, Groovy, JavaScript, PHP, C, Delphi}
\cvitem{DBMS}{\textbf{PostgreSQL}, Oracle, MySQL, MongoDB, HyTech, \textit{DB2}}
\cvitem{FTS}{\textbf{ElasticSearch}, Sphinx}
\cvitem{Servers}{\textbf{Tomcat}, Weblogic, Apache HTTPD}
\cvitem{VCS}{\textbf{Git}, Subversion}
\cvitem{Build}{\textbf{Gradle}, \textbf{Maven}}
\cvitem{CI}{\textbf{Jenkins}, \textbf{Docker}, \textbf{Artifactory}, \textbf{Zabbix}, Nexus OSS}
\cvitem{Project Management}{\textbf{Jira}, \textbf{Confluence}, \textbf{Gitlab}, Redmine, MediaWiki}
\cvitem{Numerical Computing}{Octave, Scilab}
\cvitem{Markup}{\textbf{LaTeX}, \textbf{HTML}, \textbf{CSS}}

\section{Personal Skills}
\cvlistitem{Full cycle software development experience --- business analysis, design, development, deploy and user training.}
\cvlistitem{Systematic approach for software design and development.}
\cvlistitem{Thoroughness with documents, records and acts.}
\cvlistitem{Business relations and negotiations with customers (including government).}
\cvlistitem{Preparation of reports, speeches and presentations to an audience, participation in conferences and seminars as a speaker.}
\cvlistitem{Excellent oral and written Russian language.}
\cvlistitem{Continuous professional development, lifelong learn.}
\cvlistitem{Organized, punctual, non-conflict nature.}